Learning Useful Changes\\(to Reduce Runtimes and Software Defects)

### 2015-08-20 Manuscript.tex
Updates from ShareLaTeX

 This paper uses these learners to learn methods
 to reduce defects and decrease program runtime.
 For the test data of this paper, those improvements   reduce
 the expected values of defect counts and  runtimes to    
 45\%,\%  (median) and 66\%,20\% (best case) of the initial values, respectively.
\end{abstract}
\section{Introduction}
We propose a novel {\em planning} approach called CROSSTREES for learning changes to a software system
such that its performance ``improves'', according to some measure. For  case 
studies, we apply CROSSTREES to   (1)~reduce the predicted number
of defects and (2)~reduce the runtimes of five system.

@@

Our approach is important for two reasons. Firstly, business users now demanding analytics tools that support a business-level interpretation of their data. At a panel on software analytics at ICSE’12, industrial practitioners lamented the state of the art in data mining and software engineering~\cite{menzies12a}. Panelists commented that ``prediction is all well and good, but what about decision making?''. That is, these panelists are more interested in the interpretations and follow-up that occurs after the mining, rather than just the mining itself. For example:
\bi
\item
Instead of just accepting {\em predictions} on how many software defects to expect, business users might now demand a {\em plan} to reduce the likelihood of those defects.
\item
Instead of just accepting {\em predictions} on the runtime time of their software, business users might now demand a {\em plan} to reduce that runtime. 
\ei
A second reason for the importance of our approach is, as shown below,
when asked how to change a project in order to achieve a result, it is surprisingly
difficult to use standard methods (e.g. clustering) to find those changes.
In the case study that motivated this paper, we how  standard data mining methods
can generate  seemingly
useful insights, but which are in fact completely ineffectual. On the other hand,
using CROSSTREES, we can propose changes that significantly reduce:
\bi
\item The  defects found  in Jureczko et al.'s    JAVA systems~\cite{jureczko10}.
\item The runtime of the  software    configured by  Seigmund et al.~\cite{sven12}.
\ei 
Since CROSSTREES is a somewhat novel algorithm, we present it in tutorial form.
The next section walks the reader through a sequence of approaches that start
with a standard clustering algorithm, and progresses on to CROSSTREES. The second
half of the paper then presents an extensive evaluation of CROSSTREES on 
the Jureczko  and Seigmund data sets. This is followed by notes on related work
and validity.

\section{From Clustering to  CROSSTREES}

@@

We applied planners to reduce (a) the number of defects found in Jureczko et al.'s object-oriented JAVA systems~\cite{jureczko10}; (b) the runtime of the  software systems   configured by  Seigmund et al.~\cite{sven12}. \fig{ck} shows Jureczko data attributes and \fig{cpm} shows the  Seigmund data attributes which were more diverse than the Jurecko data since they contain the results of applying many  mutators to the configuration options of the Makefiles of  BerkeleyDB (the Java  and  C versions),  Apache,  SQLite,  LLVM, and x264.

\input{tex/jur_char.tex}
\begin{figure}[!t]
\scriptsize
\begin{tabular}{llllll}
  \hline
  \rowcolor{lightgray}
Project & Domain & Lang. & LOC & Features & Config\\\hline
Berkeley DB CE & Database & C & 219,811 & 18 & 2560\\
Berkeley DB JE & Database & Java & 42,596 & 32  & 400\\
Apache & Web Server & C & 230,277 & 9 & 192\\
SQLite & Database & C & 312,625 & 39 & 3,932,160\\
LLVM & Compiler & C++ & 47,549 & 11 & 1024\\
x264 & Video Enc. & C& 45,743 & 16 & 1152\\\hline
\end{tabular}

\begin{figure}[!t]
\includegraphics[width=0.9\linewidth]{_figs/BDBC.eps}
\caption{Feature Model}\label{fig:bdbc}
\end{figure}

>>>>

 This paper uses these learners to learn methods
 to reduce defects and decrease program runtime.
 For the test data of this paper, those improvements   reduce
 the expected values of defect counts and  runtimes to    
 45\%,61.5\%  (median) and 22\%,6\% (best case) of the initial values, respectively.
\end{abstract}
\section{Introduction}
We propose a novel {\em planning} approach called CROSSTREES for learning changes to a software system
such that its performance ``improves'', according to some measure. For  case 
studies, we apply CROSSTREES to   (1)~reduce the predicted number
of defects and (2)~reduce the runtimes of five system.

@@

Our approach is important for two reasons. Firstly, business users now demanding analytics tools that support a business-level interpretation of their data. At a panel on software analytics at ICSE`12, industrial practitioners lamented the state of the art in data mining and software engineering~\cite{menzies12a}. Panelists commented that ``prediction is all well and good, but what about decision making?''. That is, these panelists are more interested in the interpretations and follow-up that occurs after the mining, rather than just the mining itself. For example:
\bi
\item
Instead of just accepting {\em predictions} on how many software defects to expect, business users might now demand a {\em plan} to reduce the likelihood of those defects.
\item
Instead of just accepting {\em predictions} on the runtime time of their software, business users might now demand a {\em plan} to reduce that runtime. 
\ei
A second reason for the importance of our approach is, as shown below,
when asked how to change a project in order to achieve a result, it is surprisingly
difficult to use standard methods (e.g. clustering) to find those changes.
In the case study that motivated this paper, we how  standard data mining methods
can generate  seemingly
useful insights, but which are in fact completely ineffectual. On the other hand,
using CROSSTREES, we can propose changes that significantly reduce:
\bi
\item The  defects found  in Jureczko et al.'s    JAVA systems~\cite{jureczko10}.
\item The runtime of the  software    configured by  Seigmund et al.~\cite{sven12}.
\ei 
Since CROSSTREES is a somewhat novel algorithm, we present it in tutorial form.
The next section walks the reader through a sequence of approaches that start
with a standard clustering algorithm, and progresses on to CROSSTREES. The second
half of the paper then presents an extensive evaluation of CROSSTREES on 
the Jureczko  and Seigmund data sets. This is followed by notes on related work
and validity.

\section{ Methods for Learning Changes}
 This paper experimentally compares four methods for inputting software project data and outputting
 recommendations on what to change.
 For case studies that illustrate how this method works, we use data from Jureczko et al.'s object-oriented JAVA systems~\cite{jureczko10} (shown in \fig{ck} and \fig{jd}) and
  software system   configuration data from by  Seigmund et al.~\cite{sven12} (see \fig{cpm}).

  The Jurecko data records number of known defects for each class, where the classes are described in terms of
  nearly two dozen metrics such as number of children, lines of code, etc.

  The Seigmund data records the runtime of compiled systems. To generate that data, Seigmund et al. perturbed
  the configuration parameters in the Makefiles of six systems: Apache, SQLite, LLVM, x264 and two versions of the
  Berkeley database (one written in ``C'' and one in Java). To ensure that the perturbations
  were valid, the option space was modeled as a tree that included knowledge of what
  options were mandatory, optional, or were alternatives (see \fig{bdbc}).
  Given those perturbations, the systems were then compiled and 
  Seigmund et al. recorded how long each perturbation took to complete a test suite.

\input{tex/jur_char.tex}

 \begin{figure}
 \scriptsize
 \begin{center}
 \begin{tabular}{r|rr}
 data set & cases & \% defective\\\hline
  ant &947& 22\\
  camel& 1819& 19\\
 jedit& 1257& 2\\
 ivy &352& 11\\
 log4j& 244 &92\\
 lucebe &442 &59\\
 poi& 936 &64\\
 synapse &379 &34\\
 velocity& 410& 34\\
 xalan& 2411& 99\\
 xerces &1055& 74
 \end{tabular}
 \end{center}
 \caption{The Jureczko data sets (columns in the format of \fig{ck}).}\label{fig:jd}
 \end{figure}

 \begin{figure}[!t]
\scriptsize
\begin{tabular}{llllll}
  \hline
  \rowcolor{lightgray}
Project & Domain & Lang. & LOC & Features & Config\\\hline
Berkeley DB CE & Database & C & 219,811 & 18 & 2560\\
Berkeley DB JE & Database & Java & 42,596 & 32  & 400\\
Apache & Web Server & C & 230,277 & 9 & 192\\
SQLite & Database & C & 312,625 & 39 & 3,932,160\\
LLVM & Compiler & C++ & 47,549 & 11 & 1024\\
x264 & Video Enc. & C& 45,743 & 16 & 1152\\\hline
\end{tabular}

\begin{figure}[!t]
\includegraphics[width=1\linewidth]{_figs/BDBC.eps}
\caption{Feature model for the Berkeley database (``C'' version). }\label{fig:bdbc}
\end{figure}

Research has shown that given the above data, it is possible to build
predictors for defective classes (in the Jureczko data) or for the runtime
of a compiled system (in the Seigmund data) (e.g. see ~\cite{sven12,nam13,he13,peters13,Menzies2013:local,me09b,me11f,me07b}).
This paper is about the next step {\em after} prediction. We envisonage as scenario
where business users are presented a prediction and they do not like what they see; e.g. the runtimes are too long of the number of defects is too high. Such users will
then ask a {\em planning}  question; i.e. ``what can we change to do better than that?'' The rest of this paper
defines and explores four methods for generating those plans.

\subsection{Method1: Centroid Deltas}

@@
